### 2020-06-02 writeup/experiments.tex

\begin{table}
\begin{minipage}[t]{.58\textwidth}
	\centering
  \begin{tabular}{c c c c c}
	\toprule
		\multirow{2}{*}{{\bf Threshold}}  & \multicolumn{2}{c}{{\bf Sentiment
		analysis}} & \multicolumn{2}{c}{{\bf ChestX-ray14}} \\
		& Precision &  Recall & Precision &  Recall \\
		\cmidrule(lr){1-1} \cmidrule(lr){2-3} \cmidrule(lr){4-5}
		0.0 & 0.596 & 1.000 & 0.593 & 1.000 \\
		0.1 & \textbf{0.756} & \textbf{0.388} & \textbf{0.738} & \textbf{0.462} \\
		0.2 & 0.919 & 0.065 & 0.875 & 0.044 \\
		% 0.3 & 1.000 & 0.004 &     - &     - \\
	\bottomrule
	\end{tabular}
	\vspace{0.1in}
	\captionof{table}{Single-task learning results can help predict postive or negative transfer in multi-task learning.}
	\label{tab:mtl_better_than_stl}
\end{minipage}
\quad
% \vspace{}
\begin{minipage}[t]{.40\textwidth}
	\centering
	\begin{tabular}{c c c}
		\toprule
		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}
		MR, SST, SUBJ, CR, MPQA, TREC\end{center}\end{minipage}} \\
		\cmidrule(lr){2-3}
		& {\bf MTL} & {\bf Alignment} \\
		\midrule
		{\bf MLP}  & 100\% & \textbf{39\%} \\
		{\bf LSTM} & \textbf{36\%} & 36\% \\
		\bottomrule
		\end{tabular}
	\vspace{0.1in}
	\captionof{table}{Measuring the data efficiency ratio of muli-task learning.}
	\label{tab:taskonomy}
\end{minipage}
\end{table}

@@

\textbf{Baseline.} We compare Algorithm \ref{alg_inc_train} to a model trained with standard multi-task learning approaches.
We measure the prediction accuracy of a particular target task.

@@

\begin{figure}[!t]
	\centering
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.975\textwidth]{figures/task_sim_norm_lstm.pdf}
		\caption{Task similarity}
		\label{fig_ab_sim}
	\end{subfigure}%
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.975\textwidth]{figures/ratio_norm_3_pairs_lstm.pdf}
		\caption{Data size}
		\label{fig_ab_data}
	\end{subfigure}
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.975\textwidth]{figures/ratio_alignment_norm_diff_all.pdf}
		\caption{Covariate shift}
		\label{fig_ab_cov}
	\end{subfigure}
	\caption{Validating the three takeaways of Section \ref{sec_insight} on sentiment analysis tasks. (a) Adding a semantically similar source task in MTL performs better than adding a dissimilar task.
	(b) As source/target data ratio increases, we observe a transition from positive to negative transfer.
	(c) As source/target data ratio increases, the performance gain from the covariance alignment procedure \cite{WZR20} over MTL increases for LSTM and MLP.}
	\label{fig_ablation}
\end{figure}

>>>>

\begin{table}
\begin{minipage}[t]{.40\textwidth}
	\centering
	\begin{tabular}{c c c}
		\toprule
		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}
		MR, SST, SUBJ, CR, MPQA, TREC\end{center}\end{minipage}} \\
		\cmidrule(lr){2-3}
		& {\bf MTL} & {\bf IncTrain} \\
		\midrule
		{\bf MLP}  & 100\% & \textbf{39\%} \\
		{\bf LSTM} & \textbf{36\%} & 36\% \\
		\bottomrule
		\end{tabular}
	\vspace{0.1in}
	\captionof{table}{Measuring the data efficiency ratio of muli-task learning.}
	\label{tab:taskonomy}
	\vspace{-0.2in}
\end{minipage}%
\quad
\begin{minipage}[t]{.58\textwidth}
	\centering
  \begin{tabular}{c c c c c}
	\toprule
		\multirow{2}{*}{{\bf Threshold}}  & \multicolumn{2}{c}{{\bf Sentiment
		analysis}} & \multicolumn{2}{c}{{\bf ChestX-ray14}} \\
		& Precision &  Recall & Precision &  Recall \\
		\cmidrule(lr){1-1} \cmidrule(lr){2-3} \cmidrule(lr){4-5}
		0.0 & 0.596 & 1.000 & 0.593 & 1.000 \\
		0.1 & \textbf{0.756} & \textbf{0.388} & \textbf{0.738} & \textbf{0.462} \\
		0.2 & 0.919 & 0.065 & 0.875 & 0.044 \\
		% 0.3 & 1.000 & 0.004 &     - &     - \\
	\bottomrule
	\end{tabular}
	\vspace{0.1in}
	\captionof{table}{Single-task learning results can help predict postive or negative transfer in multi-task learning.}
	\label{tab:mtl_better_than_stl}
	\vspace{-0.2in}
\end{minipage}
\end{table}

@@

\textbf{Training procedures and baselines.} We use round-robin training schedule for the MTL model.
We compare our incremental training scheduler of Algorithm \ref{alg_inc_train} to the round-robin training scheduler.
We focus on the prediction accuracy of a particular target task.

@@

\begin{figure}[!t]
	\centering
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.975\textwidth]{figures/task_sim_norm_lstm.pdf}
		\caption{Task similarity}
		\label{fig_ab_sim}
	\end{subfigure}%
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.975\textwidth]{figures/ratio_norm_3_pairs_lstm.pdf}
		\caption{Data size}
		\label{fig_ab_data}
	\end{subfigure}
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.975\textwidth]{figures/ratio_alignment_norm_diff_all.pdf}
		\caption{Covariate shift}
		\label{fig_ab_cov}
	\end{subfigure}
	\caption{Validating the three takeaways of Section \ref{sec_insight} on sentiment analysis tasks. (a) Adding a semantically similar source task in MTL performs better than adding a dissimilar task.
	(b) As source/target data ratio increases, we observe a transition from positive to negative transfer.
	(c) As source/target data ratio increases, the performance gain from the covariance alignment procedure \cite{WZR20} over MTL increases for LSTM and MLP.}
	\label{fig_ablation}
	\vspace{-0.15in}
\end{figure}
